14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-04-19 rules/rules19.tex
Rules: Fix

\header{Benchmark Selection.}
This track will run on all benchmarks from the \maintrack with status
\texttt{unsat}.

@@

\header{Benchmark Selection.}
This track will run on all QF\_BV benchmarks from the \maintrack with status
\texttt{sat}.

>>>>

\header{Benchmark Selection.}
This track will run on all \emph{unsatisfiable} benchmarks from the \maintrack.

@@

\header{Benchmark Selection.}
This experimental track only has one division, QF\_BV. It will run on all
\emph{satisfiable} benchmarks from this division in the \maintrack.
